Classification structurée pour l'apprentissage par renforcement inverse

### 2013-01-11 klein2012structured_RIA/revisions.tex
Prise en compte des suggestions des reviewers 2 et 3 de RIA.

@@

Some comments:
\begin{enumerate}
\item The abstract should make it more clear that your aim here is to show KTD works on both on- and off-policy settings, and with nonlinear parameterisations.

\textcolor{blue}{ The abstract has been corrected to list the qualities a good DM algorithm should exhibit.}

\item The title doesn't read very well. I would consider replacing "sole" with "single". Possibly also make it clear that you are addressing both on- and off-policy training with a single algorithm.

\textcolor{blue}{ The title has been changed to : ``An All-in-One
Reinforcement Learning Algorithm for Dialogue Management
Optimisation''.}

\item Abstract: ``Now, for each different issue was proposed a different algorithm  …". Rephrase. Maybe start "Different algorithm have been proposed to handle each different issue, making… ''.

\textcolor{blue}{We rephrased this sentence in the abstract: ``.
However, each algorithm often solves a single issue at a time while
dialogue systems exhibit all the problems at once''}

\item The paper would be much stronger with human user experiments. Simulations are known to be a poor reflection of reality. \textcolor{blue}{ Humans experiments have been lead with both DIPPER and HIS systems. The references to the related works have been added.}
\end{enumerate}

%\vspace{.5cm}
\newpage
\begin{large} \textbf{Reviewer 2:} \\ \end{large}
 Recommendation: Major Revision\\
 Comments:\\
 Summary: This paper presents an application of the recently proposed Kalman
 Temporal Differences (KTD) framework to optimize spoken dialog systems
 (SDS).  The KTD framework is claimed to enjoy benefits of (i) enabling
 off-policy learning, (ii) improving sample efficiency, (iii) facilitating
 guided exploration, (iv) adapting to nonstationary environments, and (v)
 handling nonlinear approximation architectures.  Motivated by Kalman
 filters, KTD is essentially a graphical, generative model for TD errors in
 which one is interested in inferring the (unobservable) value function.

   Two SDS are considered in experiments --- DIPPER and HIS, on which KTD is
 compared to other algoirhtms including fitted Q-learning, LSPI, and
 Q-learning.

 The KTD framework appears to be a reasonable fit to optimal control in SDS,
 given the design objectives of the framework.  Since KTD is an existing
 technique, the main contribution and novelty is therefore in its
 application to SDS.  The paper does a good job at explaining the
 motivation, and the level of technical details is appropriate for non-RL
 expert to understand most of the main idea.  Overall, the paper is quite
 easy to follow, except for some typos (see below).

 Since KTD is not new, it becomes important to have an extensive comparison
 to alternative approaches to demonstrate its pros and cons.  While a few
 natural candidates have been included, some others are ignored, and some
 may not be implemented in the best way.  Details:

\begin{enumerate}
\item  Many Bayesian RL algorithms share all (or most) claimed benefits
 of KTD.  (In fact, I think KTD may be viewed as an instance of Bayesian RL
 algorithm.)  So one wonders naturally how KTD compares to other Bayesian
 methods, say, those by Yaakov Engel (a series of papers at ICML/NIPS) and
 by Jan Peters (at ACC-08).  I am particularly wondering whether the real
 benefits here come uniquely from KTD, or from Bayesian RL in general.

\textcolor{blue}{  Precisions about how Bayesian approches differ
from the KTD approaches are given at the beginning of the Sec. III :
``It is important to notice that Kalman filtering differs from the
Bayesian filtering. Indeed, the Bayesian filtering aims at computing
the complete posterior distribution of the hidden variable while
Kalman filtering only focuses on the first and second moments of
this distribution with constrained linear update. They are equal
only when Gaussian distributions and linear parameterisations are
concerned.''. A comparison with a Bayesian algorithm (namely GPTD
proposed by Engel \textit{et al.}) has been added in the paper
Sec.~V-C (on Fig.~3 and Fig.~6).}

\item  LSPI: first, it is possible to extend it to online learning, such
 as in the AAMAS-09 paper by Lihong Li et al.

\textcolor{blue}{Thank you for the reference, we added it to our
bibliography.}

Second, ill-conditioning is
 reported in the experiments, but it is common practice to to L2-regularized
 LSTD inside LSPI.  It is not surprising that, with poor conditioning,
 LSTD/LSPI become very unstable and give bad results.  One thus wonders
 whether these algorithms are implemented in the 'right' (or robust) way to
 allow for fair comparisons.

\textcolor{blue}{Precisions about the experimental conditions when
using LSPI have been given. In particular, regularisation has
actually been tested and led to poor strategies. It is now precised}

\item Fitted Q-learning: essentially the same concerns apply as in the
 case of LSPI.

\item  The empirical results do *not* seem to be impressive.  Unless I
 misinterpret the plots, KTD-style algorithms only beat incremental
 algorithms like Q-learning and Sarsa.  Compared to other batch algorithms,
 KTD shows no significant advantage.

\textcolor{blue}{The performance of KTD is not effectively better
than those of the other batch algorithms but our goal in this
article is to propose a unique algorithm to solve several learning
issues with comparable performance. Moreover KTD processes samples
only once while other methods process them many times.}

\item In general, there is no free lunch when we come to algorithm
 selections.  KTD achieves some of the benefits at the cost of other
 disadvantages.  The paper will be more valuable to readers if the 'cons'
 are also discussed, such as convergence and optimality guarantees, to name
 a few.

\textcolor{blue}{A proof of convergence of the KTD algorithm under
certain hypothesis have been proposed (in the JAIR paper). A
difficulty appears also as far as the choice of the KTD parameters
are concerned. A paragraph about how to choose them has been added
Sec. III: `` The $\hat{\theta}_{0|0}$ vector can be initialised to a
default value or, if known, a value near the optimal one. The
$P_{0|0}$ matrix translates the certainty the user has in the prior
$\hat{\theta}_{0|0}$. It appears in Eq. (2) as a regularisation
term. A common initialisation for this matrix is $\lambda
\mathrm{Id}$. Only one parameter ($\lambda$) has thus to be chosen
instead of $p^2$ parameters ($p$ being the number of parameters to
learn).  The lower $\lambda$ the less certain is. The observation
noise $P_{n_t}$ represents the confidence about the ability of the
chosen parameterisation to represent the true Q-function.
Additionally, the evolution noise is chosen so that $P_{v_t} = \eta
P_{\theta_{t-1|t-1}}$ with $0 < \eta \ll 1$. The effect of this
heuristic is to put more emphasis on more recent data (it acts as a
forgetting factor).''. It has to be noticed that only an order of
magnitude has to be chosen. The KTD algorithm is not sensitive to
small changes in the parameters.}

\item  Furthermore, while KTD represents a reasonable algorithm, some of the
 algorithmic choices seem arbitrary and should be justified.  For example,
 the noise terms in eqn 6 are unspecified.  It may be tempting (as probably
 is done in experiments) to assume the noises are normal, but this modeling
 assumption can be quite wrong in many RL problems.  Also, more algorithmic
 details about KTD would make the paper more self-contained.  The Kalman
 gain, for instance, is quite mysterious --- how about giving a formula for
 computing that matrix after equation 7?

 \textcolor{blue}{ The KTD algorithm is now explained Sec. III: `` The KTD algorithm is done in four steps: an \textit{initialisation} step, a \textit{prediction} step, a computational phase of \textit{statistics of interest} and finally a \textit{correction} step. [$\ldots$]''. The detail of each step is then given. As precised previously, a paragraph has also been added to explain the role of the different parameters. }

\item  As said, the performance of KTD compared to fitted Q-learning or
 LSPI is not impressive.  In fact, KTD seems to converge to slightly worse
 performance.  The incremental vs. batch explanation does not make sense,
 since KTD is pretty much a batch algorithm as well --- see the authors' own
 comments on the sample efficiency of KTD below eqn 6.

\textcolor{blue}{The KTD algorithm is not a batch algorithm. The
update of the gain is done each time a sample is processed. The aim
of the article was only to propose a single algorithm to solve
different problems with performance that compares to specialised
algorithms. }

\item  What is LSPI not in any of the plots?  What is more, given the
 competitiveness of fitted Q-learning (and LSPI), I find it surprising to
 see the comparisons to them in only one experiments, but not in all (like
 in HIS).

 \textcolor{blue}{LSPI has been added to the set of curves for both systems in Fig.~1 and Fig.~2.}

\item  One of the claimed benefits of KTD is the ability to handle
 nonlinear function approximators.  In the experiments, in particular figs 5
 and 6, it is a bit sad to see nonlinear alternatives provide no benefits
 (but actually cause slower learning speed).  One then asks, at least in the
 context of SDS in this paper, why should one care about nonlinear KTD.

\textcolor{blue}{ Curves about the non-linear parameterisation have
been added to better show what happens during the learning with this
parameterisation (Fig.~4 and Fig.~8). The following explanation has
been given: ``The different runs used to compute the mean are added
on the graph. They show the detailed behaviour of the ANN. Contrary
to the linear case, the learning is either very good or very poor.
The curve representing the average results presents thus poor
results with small sets of data.''. A method should then be found to
automatically remove the worst runs like said in the conclusion.}

\item  One final comment is about the authors' prior work published at IJCAI 2011.
 It seems some results reported here have appeared in that conference
 paper.  It would avoid future confusions if the connection is made clearer.

\textcolor{blue}{The results presented in the IJCAI paper present
only an off-policy approach. This has been clarified in the
article.}

\end{enumerate}

\vspace{.5cm}
\newpage
\begin{large} \textbf{Reviewer 3:} \\ \end{large}
 Recommendation: Major Revision\\
 Comments: This paper presents how the Kalman Temporal Differences framework
 (published at JAIR by the same authors) can be applied to dialogue
 management. To show that the authors apply it to two dialogue systems one
 developed using DIPPER and one developed using the HIS dialogue management
 framework. The idea of applying the KTD framework to dialogue management is
 certainly novel and promising, however, the paper is poorly written and the
 evaluation needs to be seriously extended. The argument that because
 the algorithm performs well in simulation it should also perform well with
 real users is very weak especially for a journal submission. If things were
 so simple nobody would ever bother perform experiments with real users.

\textcolor{blue}{Our aim was not to assess that leading experiments
with simulated users is enough to prove the efficiency of the
algorithms tested. The detailed explanation of our motivation are
given Sec.~IV-A1. We precise that experiments with two differents
systems, with different state spaces, different reward functions,
different user simulation methods \textit{etc} give a good hint
about the efficiency of them and the transferability to real world
applications. In addition, DIPPER and HIS trained with the methods
we used as baselines have been tested with real users (the
references have been precised previously and added in the paper).}

 As I mentioned above the writing is not good. A lot of important details
 are missing, even simple things, like the definition of the reward
 function.

\textcolor{blue}{Indeed, we forgot to give some important details
about how the two dialogue management frameworks are cast into an
MDP. We added an entire paragraph to describe each of them (Sec.~4-A
2 \& 3). }

It is not clear to me why you compare with other existing
 algorithms only using the DIPPER-based system and not the HIS-based system.
 Is it because the HIS-based system is more complex?

\textcolor{blue}{We added others algorithms to the HIS-based system
comparison. Now, the KTD algorithm performance is compared to those
of \textit{Gaussian Process Temporal Differences} (GPTD) and
\textit{Least Square Policy Iteration} (LSPI). The GPTD algorithm is
one of the more recent and efficient algorithm for dialogue
management (references given in the article). The results are given
Fig.~2, Fig.~3 and Fig.~6.}

But this is exactly the case where one would want to use a superior algorithm. Is it because
 for example LSPI would have problems in the HIS-based system because of the
 large table that would have to be inverted? Please explain.

\textcolor{blue}{We added a description of the state space for the
HIS system in Sec.~IV-A3 and a description of the Q-function
parameterisation in Sec.~IV-C2. The number of parameters is not so
large thus we do not have matrix computation problems.}

Furthermore, I don't think anyone can manage to reproduce this experiment given that
 important details are missing. For example, the section about the
 Q-function representation is very confusing. It is unclear to me what the
 structures of the Radial Basis Function networks (one per action) are.

\textcolor{blue}{Indeed, an important part of the experimental
settings was missing. We tried to make it clearer by giving an
accurate description of them. The experimental settings are given
Sec.~V-A. The value of the parameters used for the different
algorithms have been precised for both systems so as the number of
runs to plot the different runs. We also give more details about the
Q-function representation in Sec.~IV-C. We precisely provide the
mathematical descriptions of the parameterisations.}

 Anyway, what I'm saying here, is that the authors should not expect that
 readers should have to go back and read the JAIR article because the
 missing point here is not the algorithm itself but how it is applied to
 dialogue management. Thus even if someone had understood the algorithm it's
 not clear that he would manage to apply it to dialogue management and
 reproduce the experiments presented in this paper.

\textcolor{blue}{A more accurate description of the KTD algorithm
has been given Sec.~III. The different steps of the algorithm have
been presented. A description of how the dialogue management problem
is cast into the MDP framework is in Sec.~IV-A for both systems.}

 Here are my detailed comments:

\begin{enumerate}
\item  Title: The part of the title "with a sole algorithm" sounds very weird.
 What the authors want to say is that they have developed an algorithm that
 can solve a lot of problems that previously could be solved using a variety
 of algorithms. I'm not sure what the title should be but it should
 definitely be more informative.

\textcolor{blue}{We tried to make the title clearer about what the
article is about.}

\item Introduction: Here the authors talk about different approaches to learning,
 e.g. dynamic programming, off-policy learning, on-policy learning, etc. I
 suggest they also mention the work of Henderson et al. "Hybrid
 Reinforcement/Supervised Learning of Dialogue Policies from Fixed
 Datasets", Computational Libguistics 2008. Here the authors use a hybrid
 model of SARSA-lambda and supervised learning to deal with the fact that
 there wasn't much data available for their complex state space.

\textcolor{blue}{ Thank you for the reference. We added it to the
introduction and the bibliography.}

\item Page 13, line 48: DIPPER is not a dialogue system. It is a tool that allows
 someone to write dialogue management rules. In the same way HIS is a
 dialogue management framework. So I suggest the authors say something like
 DIPPER-based and HIS-based dialogue systems instead of DIPPER and HIS
 dialogue systems. In any case, please explain the difference in the paper.

\textcolor{blue}{We modified the text accordingly.}

\item  Background: In this section, I've noticed problems with notation that can
 be confusing especially for the non-expert reader. You refer to the
 Sutton-Barto book so one would think that you would use the notation of
 Sutton-Barto. So I suggest you use r\_(t+1) instead of r\_t when you refer to
 the reward that occurs after the agent performs action a and transitions
 from state s\_t to state s\_(t+1). I'm not saying that using r\_t is wrong,
 only that it may confuse most readers that are familiar with the
 Sutton-Barto notation. Also, you use notation R(s, a, s') but you don't
 explain that it is the same as r\_(t+1). Please try to be consistent. For
 example, in equations (2) and (4) (Bellman equations) you use the notation
 R(s, a, s') but then later in section 3 you use again the Bellman equations
 with r\_t (which in my opinion should become r\_(t+1)) instead of R(s, a,
 s'). Also, sometimes you use s' and sometimes s\_(t+1). Anyway, please try
 to be consistent.

\textcolor{blue}{ The notations have been corrected to be
consistent. All the different notations introduced are now defined.}

\item Equation 4 is wrong. Near the end it should be "... gamma*max\_a'Q*(s', a')"
 (see section 3.8 in the Sutton-Barto book).

\textcolor{blue}{Thank you for mentionning this typo. We corrected
it.}

\item  In section III you need to do a better job of explaining how the KTD
 framework is applied to the dialogue management problem. For example the
 text says "the term K\_t is the Kalman gain, which depends..." Please
 explain how you calculate this. I know there is some explanation in the
 JAIR paper but you need to provide some hints in the current paper too.

\textcolor{blue}{ Some important details have been added to better
understand how the KTD algorithm works in Sec.~III. Now, the
different steps of the algorithm are precised. The definition of the
Kalman gain has been added. This gain is the one which minimises the
mean square error $J_t(\theta)$. The different parameters for the
algorithm are also given.}

\item  Then in page 17, line 38 the paper provides a very brief explanation (2
 lines) why the algorithm is sample efficient. Again, the same issue as
 before. Please provide some more information. This is one of your stronger
 points that this algorithm is sample efficient, so please explain in simple
 words why this is the case. The bottom line is that the description of the
 algorithm should be as self-sufficient as possible, minimizing the need to
 read the whole JAIR paper.

\textcolor{blue}{The classical Q-learning and SARSA algorithms are
gradient descents (first order) while KTD minimises a second error
term (second order algorithm). The convergence in the last case is
thus faster. We added this explanation at the end of the Sec.~III.}

\item In section IV, the paper says that there are no experiments with
 non-stationarity handling and yet the authors claim that this is one of the
 most important features of the algorithm. So I suggest you perform
 experiments both in simulation (with a simulated user that can change its
 goal even if it is a hand-crafted one) and with real users that change
 their goals and see how the algorithm performs. Just saying that this was
 shown in the JAIR paper is not enough because that wasn't for dialogue
 management.

\textcolor{blue}{Precisions about handling non-stationarity are
added in Sec.~III and are experimentally presented Fig.~3. When a
controlled and on-policy approach is used, handling the
non-stationarity is a good feature. Indeed, the policy used for
control varies which introduce non-stationaties.}

\item In section IV, please provide a better description of the two dialogue
 systems. For example, how many possible states do we have in each one of
 them? What are the slots and the actions used?

\textcolor{blue}{ A paragraph has been added to describe precisely
each system and how the dialogue problem is cast into the MDP
framework (state space, action space, reward function, discount
factor) in Sec.~IV-A 2 \& 3.}

\item  As I mentioned above, section IV-B is incomprehensible. You really need to
 show examples with the structure of the networks, perhaps some figures
 would help. In the same action I don't understand how you came up with the
 number 144. Also what do you mean by dimensions here, features of the
 state? Which are the 2 continuous dimensions and which are the 2 discrete
 ones?

\textcolor{blue}{We also provide now a precise description of the
two systems in Sec.~IV-A. We also added precise descriptions of the
features used to represent the Q-function in Sec.~IV-C.}

\item In section V-A the text says ``random actions are chosen among reasonable
 actions''. Could you please explain what you mean by ``reasonable actions''?

\textcolor{blue}{We precised in Sec.~V-B how the handcrafted policy
works. For the DIPPER system, a set of hand crafted rules prevents
the system from choosing actions inconsistent with the current
dialogue state. For example, it avoids to confirm a slot while it
has never has been asked before.}

\item In section V-A the text talks about comparing with LSPI but I can't see
 that in Figure 1. The LSPI graph is missing.

\textcolor{blue}{ We previously made a mistake while compiling the
graphs. We added LSPI for both DIPPER and HIS systems.}

What is the reward function
 used in the experiments of Figure 1?

\textcolor{blue}{A complete description of the rewards functions are
given Sec.~IV-A. For the DIPPER system, each dialogue turn is
penalised with a reward $-1$. At the end of the dialogue, the reward
is provided the following: $-75$ for incorrect slot filling,  $+25$
per slot filled correclty, and $-300$ if the slot is empty. For the
HIS system, the reward function penalises each dialogue turn with
$-1$. At the end of the dialogue, a reward of $+20$ is given if the
DM managed to fulfil the user request. In both cases, the dialogue
is stopped if it has more than $100$ turns. The definition of the
reward function is not an easy task. Other solutions can be
considered.}

 How come there is no variance in the
 hand-crafted graph? One would expect that the variety in the performance of
 the n-gram based simulated user would cause differences in the resulting
 dialogues.

\textcolor{blue}{The variance has not been plotted on Fig.~1 because
the error bars were too large. It has been precised in the comments
of the graphs.}

Of course that depends on what the reward function is which is
 important information not provided in the paper.

\item  For the HIS-based system, why don't you compare with LSPI, etc.? Is it
 because LSPI would be in trouble because of the larger state space? If you
 want to show that this algorithm is better than existing algorithms you'd
 better show that in a more complex system than the DIPPER-based system. You
 could perhaps try the LSPI with fast feature selection to deal with the
 large state space, see the paper by Li et al. "Reinforcement Learning for
 Dialog Management using Least-Squares Policy Iteration and Fast Feature
 Selection" Interspeech 2009.

\textcolor{blue}{Our aim was to show that one algorithm (KTD) can
perform as well as standard other ones (and sometime better) while
being generic. We added the LSPI comparison for both systems (Fig.~1
and Fig.~2). Thank you very much for he reference. We added it to
the bibliography. }

\item In Figure 2 you only show one of the behavioural policies and the KTD one.
 Is this correct? You say that there are two behavioural policies used (I
 believe the graph shows the one with greedy-exploration). Why don't you
 show both behavioural policies? And what is the reward function here?

\textcolor{blue}{We modified the figures hoping the illustration of
our points will be clearer. We also change the caption of the curves
to be more accurate.}

\item Sometimes one algorithm is trained 50 times, another 250 times, etc. Is
 there a reason you are not being consistent?

\textcolor{blue}{We precised in the article at the end of the
Sec.~V-A that there is a difference in the number of trainings
because the learning wich KTD, LSPI and GPTD algorithms takes much
more time than with Q-learning and SARSA because of matrix
inversions.}

 Also, in some figures the
 x-axis has turns and in others dialogues. Again, please try to be
 consistent or at least explain why you are not being consistent.

\textcolor{blue}{The original choice was made different for the two
systems. We precised how to make the link between the two notations
at the beginning of Sec.~V-A. For the HIS system, the length of the
dialogue can be deduced from the reward. The number of dialogue can
thus be onverted in number of samples. For example, if the mean
discounted cumulative reward is $14$ for a set of $50$ training
dialogues, since the maximum reward that can be obtained is $20$ and
that each turn a penalty of $-1$ is given, the average length of the
dialogue is $20 - 14 = 6$ turns. The number of samples is thus
approximately $6 \cdot 50 = 300$.}

\item  In Figure 3, why don't you show the hand-crafted policy?

\textcolor{blue}{Most of the figures have been modified to better
present the result. Each figure corresponds now to a particular
aspect of the KTD algorithm. We particularly paid attention to the
caption of the figures.}

 What is the reward function? Figure 4 has the same problems as Figure 2. For on-policy learning for the graphs you use a sliding windows. Do you use that for the off-policy graphs too?

\textcolor{blue}{A sliding window is only used for the controlled
approaches (Fig.~3,4,6,7,8). It has been precised in the article
when a sliding window is used. }

\item  In section V-C you talk about 22 user actions and you say "the number of
 action for the action space is 12", but earlier when you describe the
 HIS-based system you mention
 that there are 22 system actions. Please explain.
Also, in the same section you perform an experiment on handling non-linearities with the HIS-based
 system. I'd like to see that with the DIPPER-based system too.
Also, in Figure 5 what is the reward function?

\textcolor{blue}{Detailed description of the DIPPER ans HIS systems
has been given Sec.~IV.}

\end{enumerate}

\color{blue} We hope that the modifications improve the quality of
the paper. Whatever the final decision is, we would like to thank
again the reviewers for their careful reading of this paper and for
the precise and detailed comments they suggested.

Best regards,

\begin{flushright}
Lucie Daubigney, Matthieu Geist, \\ Senthilkumar Chandramohan, Olivier Pietquin.
\end{flushright}

>>>>

\newcommand{\R}{\mathcal{R}}

@@

\newpage
\begin{large} \textbf{Reviewer 2:} \\ \end{large}
\begin{itemize}
\item  On sent bien qu'il faudrait une normalisation (c'est plus ou moins esquissée par les auteurs). Sans cela la
propriété démontrée n'est pas hyper convaincante. J'encourage les auteurs à développer cet aspect esquissé page
17 (avant la section 4).\\
\textcolor{blue}{La phrase ``Ce cas est donc très improbable.'' (en parlant d'un classifieur qui renverrait un vecteur de récompense $\theta_C=0$) a été changée pour : ``Des mécanismes de régularisation dépendant du classifieur choisi peuvent être employés pour éviter cela.''. La normalisation mentionnée immédiatement après ne l'est que pour désamorcer les interrogations du lecteur quant à la présence dans la borne du terme $||\R_{\theta_c}||_\infty$. Le sujet de la régularisation de la récompense dans le cadre de l'IRL est assez subtil (du fait de la relation complexe entre récompense et valeur) et mérite un papier à part entière. Nous n'avons pas introduit ici les outils qui nous permettraient de mener cette discussion.}
\item Une troisième limitation est que je souhaiterais être convaincu de la pertinence de l'ARI. L'application à la conduite automobile est sympathique, mais que fait-on des résultats obtenus ?\\
  \textcolor{blue}{La première phrase de l'introduction a été augmentée afin de pointer plus finement vers la référence historique de l'ARI ainsi qu'une référence récente, qui expliquent l'intérêt de l'approche mieux que nous n'avons la place de le faire : ``historiquement proposée dans (Russell, 1998),
ce mécanisme trouve des applications dans divers champs, de la biologie à la neuropsychologie en passant par l’économie et plus récemment la robotique (Abbeel et al., 2010)''.}
\item Regrettons l'absence d'un état de l'art des résultats de complexité (même succinct) pour justifier le fait que l'estimation de valeur de police est plus facile que l'apprentissage par renforcement. \\
  \textcolor{blue}{Dans la section 5 (comparaison à l'existant), la note de bas de page suivante a été ajoutée : ``La résolution d'un MDP (en utilisant par exemple un algorithme d'\emph{itération de la valeur}) implique en effet de calculer de manière répétée la valeur d'une politique arbitraire. Résoudre plusieurs fois le MDP pour des récompenses arbitraires est donc beaucoup plus dur que d'estimer une fois pour toutes l'attribut moyen de l'expert.''}
\end{itemize}\vspace{1.5 em}
  \textcolor{blue}{Les typos relevées ont été corrigées.}
\vspace{.5cm}
\newpage
\begin{large} \textbf{Reviewer 3:} \\ \end{large}
\begin{itemize}
\item Alg. 1 pas clair.
\textcolor{blue}{Nous avons rajouté le nom de la fonction de score dans l'algorithme :  $s_\theta(s,a) = \theta^\top\hat{\mu}^{\pi_E}(s,a)$. Mais nous ne sommes pas sûrs que cela améliore vraiment les choses. Il semble difficile de rendre l'algorithme plus clair que ce qu'il est déjà.}
\item Les auteurs ont mégoté sur les définitions, ce qui n'est jamais bon signe; définir $\pi_1..\pi_t$.Je suppose qu'il s'agit des actions choisies aux t premiers pas de temps.
Donner l'intuition de c(t); clarifier ce qui se passe si la distribution stationnaire ne passe pas en s\\
\textcolor{blue}{Les définitions sont présentes dans le papier de Munos. Les contraintes de place et de clarté ne nous permettent pas de reprendre toute l'explication développée par celui-ci. Comme la présence des $\pi_1 etc.$ sous le signe $\max$ le laisse entendre, il s'agit de variables muettes, il peut s'agir de n'importe quelle série de politiques. La discussion sur la signification des coefficients de concentrations est présente dans le papier cité, il apparaît délicat de la paraphraser ici sans alourdir la lecture.}
\item Lemme 4.2 de Munos n'est pas ça du tout (version Hal).\\
\textcolor{blue}{Pour respecter les contraintes de places, il est attendu du lecteur qu'il fasse le développement suivant afin de justifier l'inégalité (b) :
\begin{eqnarray}
  v^{*} - v^{\pi_E} \leq \gamma P_{\pi^*}(v^*-v^{\pi_E}) + T^*
    v^{\pi_E} - v^{\pi_E}\\
    v^{*} - v^{\pi_E} - \gamma P_{\pi^*}(v^*-v^{\pi_E}) \leq T^*
    v^{\pi_E} - v^{\pi_E}\\
    (I- \gamma P_{\pi^*})(v^*-v^{\pi_E}) \leq T^*
    v^{\pi_E} - v^{\pi_E}\\
    v^*-v^{\pi_E} \leq (I- \gamma P_{\pi^*}) ^{-1}(T^*
    v^{\pi_E} - v^{\pi_E})
 \end{eqnarray}
(1) est donné par l'inégalité (a) de notre contribution, le passage de (3) à (4) se fait grâce au Lemme 4.2 du papier de Munos (dans sa version HAL).
}
\item En pratique il est satisfaisant ... p. 17. non; à la rigueur, il est suffisant...\\
  \textcolor{blue}{Changement effectué.}
\item L'erreur sur la projection des états ds l'espace des attributs moyens ; ce paragraphe pourrait être affiné en considérant la marge du cmc sous-jacent.\\
  \textcolor{blue}{Nous perdrions alors en généralité, nous considérons aussi les cmc sans marges.}
\item 4.1.
le modèle; préciser.\\
 \textcolor{blue}{ ``Le modèle ...'' devient ``Le modèle (les probabilités de transition $P$) ...''.}
 \item ligne suivante, charabia.\\
 \textcolor{blue}{ ``Soit $\Phi\in R^{|S|\times p}$ la matrice d'attributs donc les lignes contiennent les vecteurs d'attributs $\phi(s)^T$, pour tout $s\in S$.'' devient ``Soit $\Phi\in R^{|S|\times p}$ la matrice d'attributs dont les lignes sont indexées par $s\in S$ et contiennent les vecteurs d'attributs $\phi(s)^T$''.}
 \item Discuter le rapport entre gamma et la longueur N des trajectoires disponibles.\\
 \textcolor{blue}{Il n'y a pas de rapport. Nous avons pris $\gamma = 0.9$ comme le veut la coutume. Une étude superficielle (comprendre, on a joué avec sur quelques runs) ne montre pas de sensibilité évidente de l'algorithme à ce paramètre. Une étude systématique n'a pas été entreprise et ne nous semble pas extrêmement pertinente.}
\item Si on a une bonne description psi des états, pourquoi a-t-on besoin des $\mu$ ?
\textcolor{blue}{Car $\mu$ contient de l'information quant à la dynamique engendrée par la politique de l'expert.}
\item
  omettre note 1 ou ajouter des détails.
notations 2.3 $\psi(s,a)= (psi1(s,a),...)$
d'autres choix sont possibles:non. dire lesquels ou omettre la phrase.
dacile, estumation, p. 16
recontres
\textcolor{blue}{Corrections effectuées telles que suggérées.
}
\end{itemize}

\newpage

\color{blue} Encore une fois, nous remercions les reviewers et les éditeurs pour le temps passé à nous aider à améliorer notre contribution.

Cordialement,

\begin{flushright}
Edouard Klein, Matthieu Geist, \\ Bilal Piot, Olivier Pietquin.
\end{flushright}
